A Formal Model of Checked C

### 2023-01-17 sandp23/evaluation.tex
[review] inline, in-line -> in line

Our results (\fig{FIXTHIS}) show that we incur 156.6\% overhead for memory access in the WASM sandbox compared to that in a normal program.
This is inline with the observations of the recent work~\cite{jangda2019not}.

@@

As shown in~\fig{FIXTHIS}, we incur an overhead of $\sim 400\%$. This is also in-line with the performance numbers reported by prior works~\cite{jangda2019not, rlbox-paper}.
This is expected because transitioning to/from sandbox requires a context switch which is relatively more expensive than a regular function call (\ie\code{call} and~\code{ret} instruction).

>>>>

Our results (\fig{FIXTHIS}) show that we incur 156.6\% overhead for memory access in the WASM sandbox compared to that in a normal program.
This is in line with the observations of the recent work~\cite{jangda2019not}.

@@

As shown in~\fig{FIXTHIS}, we incur an overhead of $\sim 400\%$. This is also in line with the performance numbers reported by prior works~\cite{jangda2019not, rlbox-paper}.
This is expected because transitioning to/from sandbox requires a context switch which is relatively more expensive than a regular function call (\ie\code{call} and~\code{ret} instruction).
